ST563 Final Project

### 2021-04-13 ST563-FP.Rmd
Jackie Update KNN Classification

@@

@@

#### CLASSIFICATION ####
# Fit knn classification model
knn.class <- train(form.class, data = trn, method = "knn",
                   trControl=trctrl, preProcess = c("center", "scale"))

>>>>

# Load necessary libraries
library(tidyverse) # so many things
library(knitr) # making nice tables
library(caret) # training models & CV
library(leaps) # subset selection
library(corrplot) # visualize correlation
library(rmarkdown) # for output documents
library(rpart) # fitting classification tree
library(rpart.plot) # visualization of classification tree
library(randomForest) # fitting random forest model
library(kernlab) # fitting SVM
library(class) # fitting kNN model
library(glmnet) # fitting LASSO 
library(gbm) # fitting the boosted tree model
library(kableExtra) # making bolded headers for tables
library(class) #for KNN

@@

# Create Test and Training Sets
ind <- sample(length(wine$class), 0.8*length(wine$class))

@@

#### CLASSIFICATION ####
# Fit knn classification model
trn.class <- wine$class[ind]
trn.knn <- trn[,-13]
tst.knn <- tst[,-13]
knn.class <- knn(trn.knn, tst.knn, trn.class, k=5)

# Obtain confusion matrix and misclassification rate
table(knn.class, tst$class)
(37+39)/(37+39+140+104)
